Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-11 paper/paper.tex
Conclusion

\begin{figure}
\begin{center}
{\tiny
\include{figures/results_table}
}
\end{center}
\caption{Time for synthesis of machine integer benchmarks from~\cite{brahma}.
 \label{fig:results-table}}
\end{figure}

\begin{figure}
\begin{center}
{\tiny
\include{figures/icse_results_table}
}
\end{center}
\caption{Times for synthesis of machine integer benchmarks from~\cite{brahma-icse}.}
\label{fig:icse-results-table}
\end{figure}

@@

\section{Conclusion}

>>>>

\begin{figure}
\begin{center}
{\scriptsize
\include{figures/results_table}
}
\end{center}
\caption{Time for synthesis of machine integer benchmarks from~\cite{brahma}.
 \label{fig:results-table}}
\end{figure}

\begin{figure}
\begin{center}
{\scriptsize
\include{figures/icse_results_table}
}
\end{center}
\caption{Times for synthesis of machine integer benchmarks from~\cite{brahma-icse}.}
\label{fig:icse-results-table}
\end{figure}

@@

\section{Conclusion}
By expressing the program synthesis problem as a safety property for a program interpreter,
we have been able to harness the power of state of the art program analysis tools and reuse
them in a new problem domain.  We have implemented our algorithm as a freely downloadable
tool whose performance compares favourably to a state of the art program synthesiser.
Fianlly, we have taken advantage of the expressiveness of our specification language
to make an initial step towards practical synthesis of floating point programs.
